---
output: github_document
---

<!-- README.md is generated from README.Rmd -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## meNet

Cytosine methylation in the humane genome is an important and well-studied epigenetic mark that has the potential to regulate gene expression. Since the process of methylation predominantly occurs at CG dinucleotide sequences, the target of studies are these so-called CpG sites. One of the available tools, Infinium 450k assay measures the level of methylation of ~450,000 CpG sites spread across the genome. Studies suggest that CpG sites are not independent, but rather that the methylation profile is guided by the complicated network structure of CpG sites. **meNet** package utilizes prior biological knowledge and correlation analysis for reconstruction of the methylation network.

## Installation

```{r install_github, eval = FALSE}
devtools::install_github("ivabudimir/meNet")
```

For installation of vignettes together with the package, add "build_vignettes=TRUE".

## Usage

Please check [meNet](https://ivabudimir.github.io/meNet/) website.

## License

meNet is open source software, licensed under 
[GPL-3](https://github.com/ivabudimir/visProteomics/blob/master/LICENSE).
